\documentclass[twoside,11pt]{report}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{amsmath} % improve math presentation
\usepackage{graphicx, subcaption} % takes care of graphic including machinery
\usepackage{fancyhdr}
\pagestyle{fancy}
\setlength{\headheight}{14.0pt}
\usepackage[top=2.5cm, bottom=2.5cm, left=4.0cm, right=2.5cm]{geometry}
\usepackage{mathtools}
% \usepackage[margin=1in,letterpaper]{geometry} % decreases margins
\usepackage{xspace}
\usepackage{siunitx}
\usepackage{feynman}
\usepackage{pdflscape}
\usepackage{pifont}
\usepackage{booktabs}
\usepackage{ANA-FTAG-2020-08-PAPER-defs}
\usepackage[style=numeric-comp, sorting=none]{biblatex}
\addbibresource{ANA-FTAG-2020-08-PAPER.bib}
\addbibresource{Detector/Detector.bib}
\addbibresource{Reconstruction/Reconstruction.bib}
\addbibresource{DiHiggs/DiHiggs.bib}
\addbibresource{bib/ATLAS.bib}
\addbibresource{bib/CMS.bib}
\addbibresource{bib/DiHiggs_paper.bib}
\addbibresource{Theory/theory.bib}
\addbibresource{bib/ATLAS-useful.bib}
\addbibresource{bib/PubNotes.bib}
\addbibresource{bib/ConfNotes.bib}
\addbibresource{bib/ATLAS-SUSY.bib}
\addbibresource{bib/Int_note.bib}
\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file


\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{naturalnames}{hyperref}
\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage{setspace}
\usepackage{float}
\usepackage{makeidx}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{titling}
\newcommand\bjetineq{\mathop{\mbox{$b$ $\rm{jet}$}}}
\newcommand\bjetunder{\mathop{\footnotesize{\mbox{$b$ $\rm{jet}$}}}\normalsize}
\newcommand\cjetineq{\mathop{\mbox{$c$ $\rm{jet}$}}}
\newcommand\cjetunder{\mathop{\footnotesize{\mbox{$c$ $\rm{jet}$}}}\normalsize}
\setcounter{secnumdepth}{4}
\newcommand{\specialcell}[2][c]{%
 \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
\newcommand{\changefont}{\fontsize{9}{11}\selectfont}
\newcommand{\changefontbig}{\fontsize{12}{14}\selectfont}
\titleclass{\subsubsubsection}{straight}[\subsection]

\newcounter{subsubsubsection}[subsubsection]
\renewcommand\thesubsubsubsection{\thesubsubsection.\arabic{subsubsubsection}}
\renewcommand\theparagraph{\thesubsubsubsection.\arabic{paragraph}} % optional; useful if paragraphs are to be numbered

\titleformat{\subsubsubsection}
  {\normalfont\normalsize\bfseries}{\thesubsubsubsection}{1em}{}
\titlespacing*{\subsubsubsection}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{5}{\z@}%
  {3.25ex \@plus1ex \@minus.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries}}
\renewcommand\subparagraph{\@startsection{subparagraph}{6}{\parindent}%
  {3.25ex \@plus1ex \@minus .2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries}}
\def\toclevel@subsubsubsection{4}
\def\toclevel@paragraph{5}
\def\toclevel@paragraph{6}
\def\l@subsubsubsection{\@dottedtocline{4}{7em}{4em}}
\def\l@paragraph{\@dottedtocline{5}{10em}{5em}}
\def\l@subparagraph{\@dottedtocline{6}{14em}{6em}}
\makeatother


\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}

\restylefloat*{figure}
\hypersetup{
	colorlinks=true, % false: boxed links; true: colored links
	linkcolor=blue, % color of internal links
	citecolor=blue, % color of links to bibliography
	filecolor=magenta, % color of file links
	urlcolor=blue 
}


\begin{document}

\section{bbtautau paper}

The discovery of a Higgs boson ($H$) with a mass of about 125~GeV~\cite{HIGG-2012-27,CMS-HIG-12-028} 
has led to a comprehensive programme of measurements and searches by the ATLAS~\cite{PERF-2007-01} 
and CMS~\cite{CMS-TDR-08-001} collaborations at the Large Hadron Collider (LHC)~\cite{Evans:2008zzb} 
using proton--proton ($pp$) collision data. To date, all of the measured properties of the Higgs boson are found 
to be consistent with their Standard Model (SM) 
predictions~\cite{HIGG-2014-14,CMS-HIG-19-004,HIGG-2013-17-witherratum,HIGG-2019-01,HIGG-2017-06,CMS-HIG-18-002,HIGG-2018-57,CMS-HIG-17-031}, 
and no unexpected particles or Higgs boson decay modes have been observed. The SM predicts 
non-resonant $HH$ production, with approximately 90\% of the total cross-section being due 
to the gluon--gluon fusion (ggF) process. The leading-order (LO) contributions to the ggF $HH$ production are 
the `triangle diagram', which occurs via the Higgs boson self-coupling, and the heavy quark `box diagram', 
which occurs via two fermion--fermion--Higgs vertices, as shown in Figure~\ref{fig:intro:triangleAndBox}(a) and 
Figure~\ref{fig:intro:triangleAndBox}(b), respectively. 
These diagrams interfere destructively, leading to a small SM ggF $HH$ cross-section, 
which is predicted to be $31.1^{+2.1}_{-7.2}$~fb at next-to-next-to-leading (NNLO) order 
in $\alpha_s$ and including an approximation of finite top-quark-mass effects, 
for $m_H=125$~GeV and 
$\sqrt{s}=13$~\TeV~\cite{Dawson:1998py,Borowka:2016ehy,Baglio:2018lrj,deFlorian:2013jea,Shao:2013bz,deFlorian:2015moa,Grazzini:2018bsd,Baglio:2020wgt}. The vector boson fusion (VBF) process provides a sub-leading source of $HH$ production in the SM, and has a cross-section of $1.73\pm 0.04$~fb, for $m_H=125$~GeV and $\sqrt{s}=13$~TeV~\cite{Baglio:2012np,Frederix:2014hta,Ling:2014sne,Dreyer:2018rfu,Dreyer:2018qbw}. Due to this small cross-section, an observation of SM non-resonant $HH$ production is not expected with the currently available LHC data set, though significant non-resonant and resonant enhancements to the $HH$ cross-section are predicted in many beyond-the-SM (BSM) theories.% https://twiki.cern.ch/twiki/bin/view/LHCPhysics/LHCHWGHH?redirectedfrom=LHCPhysics.LHCHXSWGHH#Latest_recommendations_for_gluon. $31.05^{+2.2\%}_{-5.0\%}\text{(scale)}\pm 3.0\%\text{(PDF}+\alpha_s\text{)}\pm 2.1\%\text{(}\alpha_s\text{)}\pm 2.6\%\text{(}m_\text{top}~\text{approx)}^{+4\%}_{-18\%}\text{(}m_\text{top}\text{)}$~fb. $1.726^{+0.03\%}_{-0.04\%}\text{(scale)}\pm 2.1\%\text{(PDF+}\alpha_s\text{)}$~fb. $1.726^{+0.03\%}_{-0.04\%}\text{(scale)}\pm 2.1\%\text{(PDF+}\alpha_s\text{)}$~fb
Due to the diagram shown in Figure~\ref{fig:intro:triangleAndBox}(a) and its interference 
with the diagram shown in Figure~\ref{fig:intro:triangleAndBox}(b), non-resonant $HH$ production is 
a sensitive probe of the Higgs boson trilinear self-coupling and the shape of the Higgs field potential, 
which have important implications for the stability of the electroweak vacuum~\cite{Branchina:2008pc,Buttazzo:2013uya}, 
baryogenesis~\cite{Reichert:2017puo}, and inflation~\cite{Bezrukov:2007ep,Masina:2011aa}. 
Modifications to the non-resonant $HH$ cross-section occur in BSM scenarios with new, 
light, coloured scalars~\cite{Kribs:2012kz}, composite Higgs models~\cite{Grober:2010yv}, 
theoretical scenarios with couplings between pairs of top-quarks and pairs of Higgs bosons~\cite{Contino:2012xk}, 
as well as models with a modified coupling of the Higgs boson to the top-quark. 
Previous searches for non-resonant $HH$ production by ATLAS and CMS have been performed in 
the $b\bar b\tau^+\tau^-$~\cite{HIGG-2016-16-witherratum,CMS-HIG-17-002}, 
$b\bar b\gamma\gamma$~\cite{HIGG-2016-15,Sirunyan:2020xok}, $b\bar bb\bar b$~\cite{EXOT-2016-31,CMS-HIG-17-017}, 
$b\bar b\ell^+\nu\ell^-\nu$~\cite{HDBS-2018-33,CMS-HIG-17-006} decay channels, 
by ATLAS in the $b\bar bqq\ell\nu$~\cite{HIGG-2016-27}, $WW^*\gamma\gamma$~\cite{HIGG-2016-20} 
and $WW^*WW^*$~\cite{HIGG-2016-24} decay channels, and by CMS in the $b\bar bWW^*/b\bar bZZ^*$~\cite{CMS-HIG-17-006} 
decay channel. In the $b\bar b\tau^+\tau^-$ decay channel, ATLAS and CMS set observed (expected) upper 
limits on the non-resonant $HH$ production cross-section of 12.7 (14.8)~\cite{HIGG-2016-16-witherratum} 
and 30 (25)~\cite{CMS-HIG-17-002} times the SM expectation using 36.1~\ifb\ and 35.9~\ifb\ of 
13~TeV $pp$ collision data, respectively. Using these data sets, ATLAS and CMS performed combinations of 
several search channels improving these observed (expected) limits to 6.9 (10)~\cite{HDBS-2018-58} 
and 22.2 (12.8)~\cite{CMS-HIG-17-030} times the SM expectation, respectively. 
ATLAS and CMS recently published searches for $HH$ production in the $b\bar b\gamma\gamma$ 
decay mode using their full Run-2 $pp$ collision data sets, which set observed (expected) 
upper limits on the SM non-resonant $HH$ cross-section of 4.1 (5.5) and 5.2 (7.7) times the SM expectation, 
respectively~\cite{ATLAS-CONF-2021-016,CMS:2020tkr}. CMS also recently published a search for $HH$ production 
in the $b\bar bb\bar b$ decay mode using their full Run-2 $pp$ collision data set, 
which set an observed (expected) upper limit on the SM non-resonant $HH$ cross-section of 3.6 (7.3) times 
the SM expectation~\cite{CMS-PAS-HIG-20-005}.% in the $b\bar b\tau^+\tau^-$~\cite{HIGG-2016-16-witherratum,CMS-HIG-17-002}, $b\bar b\gamma\gamma$~\cite{HIGG-2016-15,CMS-HIG-17-008}, $b\bar bb\bar b$~\cite{Aaboud:2018knk,Sirunyan:2018tki}, $b\bar bVV^*$~\cite{HIGG-2016-27,CMS-HIG-17-006}, $WW^*\gamma\gamma$~\cite{HIGG-2016-20}, and $VV^*VV^*$~\cite{HIGG-2016-24} decay channels.
Various BSM scenarios predict heavy resonances that can decay to pairs of Higgs bosons. 
These BSM resonances include heavy Higgs bosons from extended Higgs sectors such as two Higgs doublet 
models (2HDMs)~\cite{Branco:2011iw}, the minimal supersymmetric extension of the 
SM~\cite{HABER198575,DIMOPOULOS1981150}, twin Higgs models~\cite{Chacko:2005vw}, 
and composite Higgs models~\cite{Grober:2010yv,Mrazek:2011iu}. Heavy resonances that decay 
to pairs of Higgs bosons also include spin-0 radions and spin-2 gravitons from the 
Randall--Sundrum model~\cite{Randall:1999ee,Tang:2012pv,Cheung:2000rw}, 
and stoponium states in supersymmetric models~\cite{Kumar:2014bca}. 
Searches for resonant $HH$ production have been performed in many final states by ATLAS and CMS, 
and no significant excesses have been 
observed~\cite{HIGG-2016-16-witherratum,CMS-HIG-17-002,HIGG-2016-15,CMS-HIG-17-008,ATLAS-CONF-2021-035,HIGG-2016-27,CMS-HIG-17-006,HIGG-2016-20,HIGG-2016-24,HDBS-2018-58,CMS-HIG-17-030}.% EXOT-2016-31
This paper describes a search for non-resonant and resonant $HH$ production 
in the final state with two jets containing $b$-hadrons ($b$-jets) and two $\tau$-leptons. 
A sizeable fraction of all possible final states predicted by the SM, 
$\mathcal{B}(HH\to b\bar b\tau^+\tau^-)=7.3\%$~\cite{deFlorian:2016spz}, 
and relatively low backgrounds make this one of the most sensitive $HH$ search signatures. 
In the search for non-resonant $HH$ production, the signal is assumed to have SM-like kinematics, 
and the search is optimised for maximum sensitivity to the 
cross-section rather than the Higgs boson self-coupling. 
Additionally, only the ggF and VBF non-resonant $HH$ production modes are considered, 
because other production modes are not expected to contribute significant 
additional sensitivity in this search. 
A narrow-width CP-even scalar particle ($X$) with a mass between 251 and 
1600~GeV is used as the benchmark model for the resonant signal. 
Decay modes in which both $\tau$-leptons decay hadronically ($\tau_\text{had}$), 
and in which one decays hadronically and the other leptonically ($\tau_\text{lep}$), 
are both considered; these are referred to 
as $\tau_\text{had}\tau_\text{had}$ and $\tau_\text{lep}\tau_\text{had}$, respectively. 
The presence of $\tau_\text{had}$ are determined by their visible decay products ($\tau_\text{had-vis}$). 
Events are categorised based on the type of trigger that accepted the event, 
and are required to contain two oppositely charged $\tau_\text{had-vis}$ 
and two $b$-tagged jets in the $\tau_\text{had}\tau_\text{had}$ final state, 
or an electron or muon and an oppositely charged $\tau_\text{had-vis}$ and 
two $b$-tagged jets in the $\tau_\text{lep}\tau_\text{had}$ final state. 
Signal events also contain neutrinos from the decay of $\tau$-leptons and $b$-hadrons, 
which manifest themselves as missing momentum transverse to the beamline ($\mathbf{p}_\text{T}^\text{miss}$). 
Backgrounds in this search include top-quark pairs ($t\bar t$), single top-quarks, 
$W$ and $Z$~bosons in association with jets, diboson processes ($WW$,$WZ$,$ZZ$), 
single Higgs bosons, and multi-jet production. 
In some background events, quark- or gluon-initiated jets are misidentified as $\tau_\text{had-vis}$. 
The selected events are tested for the presence of the signal 
by performing profile-likelihood fits to multivariate discriminant distributions. 
The search is performed using the Run~2 $pp$ collision data set,
delivered between 2015 and 2018 at a centre-of-mass energy $\sqrt{s}=13$~TeV by the LHC. 
The data were collected by the ATLAS detector~\cite{PERF-2007-01} 
and correspond to an integrated luminosity of 139~\ifb. 
Compared to the previous ATLAS result~\cite{HIGG-2016-16-witherratum}, 
in addition to the greater integrated luminosity,
this search profits from improved $\tau_\text{had-vis}$ and $b$-jet 
reconstruction and identification, more sophisticated multivariate techniques 
used to target the resonant signal hypotheses, and new background estimation techniques.
In particular, the combined reconstruction and identification 
efficiencies for $\tau_\text{had-vis}$ and $b$-jets increased by 
around 25--38\% and 10\%, respectively.% , and single LQ production is not considered as it is expected to have a lower cross-section than LQ pair production~\cite{} % . The $HH\to b\bar b\tau^+\tau^-$ decay mode profits from a large branching fraction of 7.4\%, and relatively low backgrounds. %  Vector LQs are not considered in this paper as they are less easily probed in a model independent way~\cite{Mandal:2019gff}. Neutrinos are produced in decays of $\tau$-leptons decays are reconstructed as missing momentum transverse to the beamline ($E_\text{T}^\text{miss}$). 
%% Events are categorised based on which trigger accepted the event, and are required to contain two $b$-jets, as well as two oppositely charged hadronic $\tau$-leptons ($\tau_\text{had-vis}$) in the $\tau_\text{had}\tau_\text{had}$ final state, or an electron or muon and an oppositely charged $\tau_\text{had-vis}$ in the $\tau_\text{lep}\tau_\text{had}$ final state. Single $b$-jet categories are also used in the LQ search. The signal in all channels is extracted from backgrounds of $t\bar t$ and single top, QCD jets, $W$ boson, $Z$ boson, and single Higgs bosons using fits to neural network--based discriminants.% categorised in the $\tau_\text{had}\tau_\text{had}$ and $\tau_\text{lep}\tau_\text{had}$ final states, and





\section{klambda scan}
This note presents a combination of searches for Higgs boson pair production using 
126--139\ifb of 
proton-proton collision data recorded with the ATLAS detector at a center-of-mass energy of 
$\sqrt{s}=\SI{13}{\tev}$ at the LHC. Three searches for pairs of Higgs bosons, 
in the $b\bar{b}\gamma\gamma$, $b\bar{b}\tau^{+}\tau^{-}$, and $b\bar{b}b\bar{b}$ 
final states, are included in this combination. 
The non-resonant interpretation uses results from the $b\bar{b}\gamma\gamma$ and $b\bar{b}\tau^{+}\tau^{-}$ searches, while the resonant interpretation uses results from all three searches. No statistically significant excess above the Standard Model expectation has been found. 
Upper limits are set on the production rate of non-resonant Higgs boson pairs, at the 95\% confidence level, assuming Standard Model kinematics. The observed (expected) combined upper limit is found to be 3.1 (3.1) times the Standard Model prediction.
%Observed (expected) upper limits of \2.0 fb (\2.2 fb) are set on the non-resonant Higgs boson pair production cross-section, at the 95\% confidence level, assuming Standard Model kinematics. The observed (expected) combined upper limit on the di-Higgs signal strength was found to be 3.1 (3.1). 
The value of the Higgs boson trilinear self-coupling modifier 
$\kappa_{\lambda} \equiv \lambda_{HHH}/\lambda_{\mathrm{SM}}$ is excluded outside the observed (expected) range 
$-1.0 \le \kappa_{\lambda} \le 6.6$ ($-1.2 \le \kappa_{\lambda} \le 7.2$) 
at 95\% confidence level. Upper limits on the production cross-section of a heavy scalar resonance decaying 
to two Standard Model Higgs bosons are set at 95\% confidence level between 
1.1 and 595 fb (1.2 and 392 fb) in observation (expectation), 
depending on the resonance mass, $m_X$, within the studied mass 
range $\SI{251}{\gev}\le m_X \le\SI{3}{\tev}$.  


Since the discovery of the Higgs boson ($H$) at the Large Hadron Collider (LHC) in 2012~\cite{HIGG-2012-27,CMS-HIG-12-028}, a priority of the ATLAS and CMS collaborations has been to better understand its properties and couplings. The Higgs boson self-coupling is directly related to the shape of the Higgs scalar field potential, which is important for understanding the mechanism of electroweak symmetry breaking, and serves as a precision test of the electroweak theory. Higgs boson pair (\HH) production provides a direct probe of the Higgs boson self-coupling, which has a direct effect on the size of the \HH production cross-section. 

In the Standard Model (SM), the gluon--gluon fusion process (ggF) 
accounts for more than 90\% of non-resonant \HH production. It proceeds mainly through two diagrams at leading order (LO)~\cite{Glover:183945}, known as the triangle diagram and the box diagram, which are shown in Figure~\ref{fig:feyn_sm_hh}. The former is the LO diagram which is sensitive to the Higgs boson trilinear self-coupling~$\lambda_{HHH}$. These diagrams interfere destructively, leading to a small SM \HH cross-section, which is three orders of magnitude smaller than single Higgs boson production.
The SM \HH cross-section is predicted to be $\sigma_{\textrm{ggF}}^\textrm{SM}(HH) = 31.05^{+6\%}_{-23\%} (\textrm{scale} + m_{\textrm{top}}) \pm{3.0\%} (\textrm{PDF}+\alpha_{s})$~fb~\cite{Dawson_1998,Borowka:2016ehy,Baglio_2019,de_Florian_2013,Shao_2013,deflorian2015higgs,Grazzini_2018,Baglio_2021} at next-to-next-to-leading order (NNLO) in $\alpha_s$ and including an approximation of finite top-quark-mass effects, for the Higgs boson mass $m_H=125$~GeV and $\sqrt{s}=13$~\TeV. 
The ``$\textrm{PDF}+\alpha_{s}$'' uncertainty accounts for the effects of the strong coupling constant and parton distribution functions, the ``scale'' uncertainty is due to the finite order of quantum chromodynamics (QCD) calculations, and the  ``$m_{\textrm{top}}$'' uncertainty is related to the top-quark mass scheme.

The next leading \HH production mode is Vector Boson Fusion (VBF), contributing 5\% of the SM \HH production rate. The cross-section of the VBF \HH process is evaluated at next-to-next-to-next-to-leading order (N3LO) in QCD~\cite{Baglio_2013,Frederix_2014,Liu-Sheng:2014gxa,Dreyer:2018qbw,Dreyer:2018rfu}, with a value of $\sigma_{\mathrm{VBF}}^\textrm{SM}(HH) = 1.73^{+0.03\%}_{-0.04\%}\,\text{(scale)}\,\pm 2.1\%\,(\textrm{PDF}+\alpha_{s})$~fb, for $m_H=125$~GeV and $\sqrt{s}=13$~TeV. The tree-level VBF \HH diagrams are shown in Figure~\ref{fig:feyn_sm_vbf_hh}. Figure~\ref{fig:feyn_sm_vbf_hh}(a) involves the Higgs boson self-coupling, while the other two involve solely the Higgs boson's couplings to vector bosons.


% Resonant \HH production or an enhancement of the non-resonant \HH production rate may be observable with the full Run-2 dataset, and would point to Beyond the Standard Model (BSM) physics. 
The non-resonant \HH production rate is very sensitive to small anomalous couplings in Beyond the Standard Model (BSM) scenarios. For example, changing the sign of the Higgs boson trilinear self-coupling with respect to the Standard Model expectation would quadruple the \HH production rate~\cite{Baglio_2013}. It is estimated that the Higgs boson trilinear self-coupling can be measured to a precision of 50\% at the HL-LHC~\cite{Cepeda:2019klc} by combining results from both ATLAS and CMS. 

Pairs of Higgs bosons can also be produced via the decay of a hypothetical heavy resonance, and many BSM theories predict the existence of such heavy particles. Models that predict additional scalars include: electroweak singlet models~\cite{Hill:1987ea, Robens:2015gla}, two-Higgs-doublet models~\cite{THDM}, and models inspired by the Minimal Supersymmetric Standard Model (MSSM) such as the hMSSM~\cite{ Djouadi:2005gj, Djouadi:2013vqa, Djouadi:2013uqa, Djouadi:2015jea}. The leading order Feynman diagram corresponding to the production of a heavy scalar particle $X$ decaying to a pair of Higgs bosons is shown in Figure~\ref{fig:feyn_resonance}. Only the ggF production mode is considered in this note.



% \subsection{Scope of this preliminary \HH combination}
% This note presents a combination of searches for non-resonant and resonant Higgs boson pair production using the full Run-2 LHC dataset, corresponding to an integrated luminosity of up to \SI{139}{\ifb} of data collected at $\sqrt{s}=13$~\TeV. It includes a combination of non-resonant \HH to \bbyy and \bbtautau searches and a combination of resonant \HH to \bbbb, \bbtt and \bbyy searches. A Higgs boson mass of \SI{125.0}{\gev} is assumed.

% A previous ATLAS combination of searches for non-resonant and resonant \HH pair production was performed on a partial Run-2 dataset, using up to 36.1\,fb$^{-1}$ of data~\cite{HDBS-2018-58}. It included six channels: \bbbb~\cite{EXOT-2016-31}, \bbtautau~\cite{HIGG-2016-16}, \bbyy~\cite{HIGG-2016-15}, $W^+W^-W^+W^-$~\cite{HIGG-2016-24}, \bbWW~\cite{HIGG-2016-27} and $W^+W^-\gamma\gamma$~\cite{HIGG-2016-20}.
% % It provided limits on the \HH production cross-section $\sigma_{HH}$ for the SM case and as a function of $\kl$, and on the production cross-section of a narrow-width scalar resonance $X$ decaying to \HH.
% The combined observed (expected) limit for non-resonant \HH production at 95\% confidence level was 6.9 (10) times the predicted Standard Model cross-section. When varying the Higgs boson trilinear self-coupling from its Standard Model value, the allowed range for the self-coupling modifier $\kl \equiv \lambda_{HHH}/\lambdaSM$ was observed (expected) to be $-5.0 \le \kl \le 12.0$ ($-5.8 \le \kl \le 12.0$). Limits were also presented on the production cross-section of a narrow-width scalar resonance $X$, in the mass range 260--\SI{3000}{\gev}, decaying to \HH.
% CMS also published a combination of \HH searches using the partial Run-2 dataset, up to 35.9\,fb$^{-1}$ of data~\cite{CMS-HIG-17-030}. The CMS combined observed (expected) limit for non-resonant \HH production at 95\% confidence level was 22.2 (12.8) times the predicted Standard Model cross-section, and the observed (expected) allowed range for the self-coupling modifier \kl was $-11.8 \le \kl \le 18.8$ ($-7.1 \le \kl \le 13.6$). Limits on resonant \HH production, in the mass range 250--\SI{3000}{\gev}, were also presented.
\section{Higg EFT}
This study presents limits on Higgs Effective Field Theory (HEFT) benchmark models 
and couplings based on the searches for $HH$ production in the \bbyy and \bbtautau final states, 
and their combination. The searches make use of $139$ $\textrm{fb}^{-1}$ of proton-proton collision 
data recorded with the ATLAS detector at a centre-of-mass energy of $\sqrt{s}=13$ TeV at the LHC. 
Upper limits on the $HH$ production cross-section are set on seven HEFT benchmark models at the $95$\% confidence level, 
with observed (expected) limits ranging from $50.2$ ($45.5$) fb to $133.6$ ($133.5$) fb. 
Exclusion limits are also set on two beyond the Standard Model (SM) coupling parameters, 
$c_{gghh}$ and $c_{tthh}$, described in HEFT, excluding values outside the observed (expected) 
ranges of [$-0.3, 0.4$] ([$-0.3, 0.3$]) and [$-0.2, 0.6$] ([$-0.2, 0.6$]), respectively, at the 95\% confidence level.

The Higgs Boson $(H)$, a cornerstone of the SM, was discovered by the ATLAS and CMS collaborations in 2012 \cite{HIGG-2012-27,CMS-HIG-12-028}. 
Numerous measurements of its spin and couplings have been 
performed \cite{HIGG-2013-17-witherratum,CMS-HIG-14-018,ATLAS-CONF-2020-027} since its discovery, 
showing consistency with SM predictions. The Higgs boson self-coupling, $\lambda_{HHH}$, provides 
direct access to the shape of the Higgs potential, and its measurement is a primary physics goal of 
the LHC and its forthcoming upgrade, the High Luminosity LHC. Modifications to the Higgs boson self-coupling can 
occur through beyond the SM (BSM) physics, which can lead to an enhancement of the rate of Higgs boson 
pair-production and modifications of the kinematics of the process. 
%BSM enhancements can occur through either resonant processes ($X\rightarrow HH$) or through non-resonant processes, with this document focusing on the latter. 
\newline

% Introduce HEFT

%Effective Field Theories (EFT) are low energy approximations to more complicated underlying theories which describe physical phenomena occurring at a much higher energy scale and

Effective Field Theories (EFT) provide a model-independent approach to parametrise the effects of 
candidate BSM theories that reduce to the SM at low energies. Two different EFT formalisms are 
widely described in the literature~\cite{MICCO2020100045, Grzadkowski:2010es, Cohen:2020xca}: 
the SM EFT and the Higgs EFT (HEFT). This note focuses on the HEFT framework, where the 
Lagrangian is organised following the guidance of chiral perturbation theory and 
where the low-energy dynamics of electroweak symmetry breaking are described using a nonlinear 
realization of $SU(2)\times U(1)$. In this formalism, anomalous Higgs boson couplings are 
expected to be the dominant effects on new physics in the electroweak sector.
Deviations from SM predictions can potentially be observed via $HH$ production using the HEFT framework.
\newline



\end{document}