The following sources of uncertainties are considered for the data-driven multi-jet estimation in the LQ $\tau_{had}\tau_{had}$ channel: %, described in Section~\ref{subsec:HadHadmultijet}:
\begin{itemize}
\item statistical uncertainties on the FFs.
\item uncertainties on the difference between using FFs derived from 1+2-$b$tag inclusive region and FFs derived from 1-$b$-tag only region and TFs are used in 2-$b$-tag region as HH hadhad case.
\item background subtraction.
\end{itemize}

Statistical uncertainties on the FFs are estimated by moving FFs by 1 up/down for statistical errors shown in ~\Cref{fig:lq_hadhad_fake_factors}.
Comparing final yield of multijet fake events in LQ \hadhad SR, the size of this uncertainty is estimated as $\pm 6.92 \%$. The shape difference is considered.

The effect of the difference of FFs derived from 1+2-b-tag inclusive region and from 1-b-tag region only with TFs are evaluated
by comparing final yield of multijet fake events in LQ \hadhad SR estimated by these two cases. The size of this uncertainty is estimated as 
$\pm 15.6 \%$, and the shape difference is considered.

The uncertainty due to the subtraction of non-multi-jet backgrounds in the 2-tag OS Anti-ID region is split into the origin of
the dominant backgrounds that are being subtracted: true \tauhad \ttbar, fake \tauhad \ttbar, and other (predominantely V+jets / single-top).

The subtraction uncertainty of true \tauhad \ttbar is estimated by comparing the nominal prediction of \ttbar (true \tauhad) with
the uncertainty prescriptions for the \ttbar-process by PMG in the 2-tag OS Anti-ID region. The breakdown of uncertainties is depicted in~\Cref{tab:LQ_systematics_multijet_hh_ttbar_subtraction}. The fake estimate variations are provided by varying the subtraction of 
true \tauhad \ttbar by the total uncertainty ($\substack{+19.7 \% \\ -24.6 \%}$) in the 2-tag OS Anti-ID region when estimating the multi-jet 
fake background. The impact on the normalization of the fake template after true \tauhad \ttbar subtraction is +0.280 -0.224.

\begin{table}[htbp]
  \centering
  \begin{tabular}{lr}
    \toprule
    Source & Uncertainty \\
    \midrule
    ME & $\pm 9.98$ \\[0.3em]
    PS & $\pm 12.6 \%$ \\[0.3em]
    $\mu_\text{R}$ & $\substack{+9.92 \% \\ -9.39 \%}$ \\[0.3em]
    $\mu_\text{F}$ & $\substack{+3.49 \% \\ -2.83 \%}$ \\[0.3em]
    ISR & $\substack{+1.89 \% \\ -12.2 \%}$ \\[0.3em]
    FSR & $\substack{+4.13 \% \\ -9.97 \%}$ \\
    \midrule
    Total & $\substack{+19.7 \% \\ -24.6 \%}$ \\
    \bottomrule
  \end{tabular}
  \caption{Uncertainty on true \tauhad \ttbar in the 2-tag OS Anti-ID region.}
  \label{tab:LQ_systematics_multijet_hh_ttbar_subtraction}
\end{table}

The subtraction uncertainty of fake \tauhad \ttbar is estimated using the dedicated scale factor measurement introduced in~\Cref{subsec:LQLepHadttbarfake}.
%%The variance of the scale factor measurement is dominated by the leading eigenvariations due to the large correlations of the scale factors measured in the Anti-ID region.
%%Therefore, only the leading eigenvariation for every offline \tauhad identification and trigger setup is propagated to the fake estimate.
%%Moreover, due to the limited set of experimental uncertainties used for the scale factor measurement in the Anti-ID region,
%%the full difference of the scale factors to 1 is taken as an additional uncertainty and propagated to the fake estimate.
A breakdown of the normalization impact is shown in~\Cref{tab:LQ_systematics_multijet_hh_fake_ttbar_subtraction}. {\color{red} to be evaluated, depend on the anti-tau ID SF measurement.}.
The shape impact of the individual NPs is propagated to the fit.

%% \begin{table}[htbp]
%%   \centering
%%   \begin{tabular}{lr}
%%     \toprule
%%     Nuisance Parameter & Impact on multi-jet fake yield \\
%%     \midrule
%%     \texttt{TTBAR\_FAKESF\_ANTITAU\_OFFL\_EIGEN0} & $\pm 0.09 \%$ \\
%%     \texttt{TTBAR\_FAKESF\_ANTITAU\_TAU25\_EIGEN0} & $\pm 3.97 \%$ \\
%%     \texttt{TTBAR\_FAKESF\_ANTITAU\_TAU25EF\_EIGEN0} & $\pm 2.05 \%$ \\
%%     \texttt{TTBAR\_FAKESF\_ANTITAU\_TAU25RNN\_EIGEN0} & $\pm 4.71 \%$ \\
%%     \texttt{TTBAR\_FAKESF\_ANTITAU\_DIFF} & $\pm 2.00 \%$ \\
%%     \midrule
%%     Total & $\pm 6.80 \%$ \\
%%     \bottomrule
%%   \end{tabular}
%%   \caption{Normalization impact of fake \tauhad subtraction uncertainties on the fake estimate.}
%%   \label{tab:systematics_multijet_hh_fake_ttbar_subtraction}
%% \end{table}

Due to the small relative subtraction of other backgrounds, which are predominantely composed of V+jets and single-top events,
a conservative estimate of the subtraction uncertainty is defined by varying the subtraction of these backgrounds up and down by $50\%$. 
This has an impact of $\pm 30.6 \%$ on the final multi-jet fake estimate. The shape uncertainty of the subtraction is propagated to the fit.

The uncertainty on the normalisation of the multi-jet background is summarized in~\Cref{tab:LQ_systematics_multijet_uncertainty}, and XX\% in total.
{\color{red} to be evaluated, depend on the anti-tau ID SF measurement.}.

\begin{table}[htbp]
  \centering
  \begin{tabular}{lr}
    \toprule
    Source & Uncertainty \\
    \midrule
    FF statistics & $\pm 6.92\%$ \\[0.3em]
    FF region difference & $\pm 15.6 \%$ \\[0.3em]
    true ttbar subtraction & $+28.0\%, -22.4\%$ \\[0.3em]
    fake ttbar subtraction & $XX\%$ \\[0.3em]
    other background subtraction & $\pm 30.6\%$ \\[0.3em]
    \midrule
    Total & $XX\%$ \\
    \bottomrule
  \end{tabular}
  \caption{Uncertainty on multijet fake estimation uncertainty for LQ \hadhad channel.}
  \label{tab:LQ_systematics_multijet_uncertainty}
\end{table}

