Cross section and BR uncertainties are applied to all single-Higgs processes included in the analysis as backgrounds (following recommendations from LHC Higgs Working Group). In addition to those, a 100\% uncertainty is applied on the normalisation of the single-Higgs processes without real $b$-quarks (ggFHtautau, VBFHtautau and WHtautau) to account for modelling of Higgs processes in association with extra heavy flavor (conservative uncertainty motivated by studies of heavy-flavour production in association with top-quark pairs~\cite{PhysRevD.89.072012} and W boson production in association with b-jets~\cite{Aad_2013} and from more recent ttHyy studies~\cite{MorenoLlacer:2684286}, applied in all di-Higgs analyses where relevant). No heavy-flavour uncertainty is assigned to the ttH and ZH production modes, where the dominant heavy-flavour contribution is already accounted for in the LO process.

Acceptance uncertainties on ttH and ZH are evaluated in the phase-space of the signal regions of this analysis by MC-to-MC comparison.

Uncertainties due to PDF, $\alpha_s$ and scales are evaluated using internal alternative weights present in all the single-Higgs nominal samples. 

For PDF and $\alpha_s$ variations, the PDF4LHC\_ NLO\_ 30 uncertainty sets, consisting of 30 eigenvectors parameterising the uncertainties for all the PDFs and 1 parameter for the $\alpha_s$ variations, are used and are compared to the nominal PDF4LHC\_ NLO \_ 30 to evaluate the size of the variations (as recommended by the Higgs group even if the nominal PDF used in the nominal sample is the NNPDF30NNLO PDF set). These variations are combined following the PDF4LHC recommendations~\cite{Butterworth:2015oua}, consisting in evaluating the PDF uncertainty $\delta_{PDF}$ by calculating the square root of the sum in quadrature of the 30 variations, evaluating the $\alpha_s$ uncertainty by taking the half difference between the same PDF set with two different $\alpha_s$ values, and then adding in quadrature the two contributions of $\delta_{PDF}$ and $\alpha_s$ uncertainties to obtain the total uncertainty, in each bin of the PNN score distribution.

Variations of the renormalisation and factorisation scales are used to estimate the uncertainty due to missing higher order corrections. For these scale variations, the 7-point scale variations of the renormalisation ($\mu_R$) and the factorisation scale ($\mu_F$) are used and they are combined by taking an envelope of all of the variations (as recommended by the Physics Modelling group), in each bin of the PNN score distribution.

Parton shower hadronisation algorithmic uncertainties are evaluated comparing samples showered with Pythia and Herwig (with the ME provided by the same generator) to have an handle on the differences between the PS and non-perturbative models as Pythia and Herwig use different algorithms for the parton shower and for the non-perturbative modeling (hadronisation, MPI). The list of single-Higgs alternative samples used for PS uncertainties is given in Table~\ref{sec:systs:tab:systematics_singleHiggssamples_PS}.

\begin{table}
\centering
\begin{tabular}{|c|c|}
\hline
DSID & Name\\
\hline
346346 & PhH7EG\_ H7UE\_ NNPDF30ME\_ ttH125\_ allhad\\
346347 & PhH7EG\_ H7UE\_ NNPDF30ME\_ ttH125\_ semilep\\
346348 & PhH7EG\_ H7UE\_ NNPDF30ME\_ ttH125\_ dilep\\
346397 & PowhegHerwig7EvtGen\_ NNPDF3\_ AZNLO\_ ZH125J\_ MINLO\_ llbb\_ VpT\\
346399 & PowhegHerwig7EvtGen\_ NNPDF3\_ AZNLO\_ ggZH125J\_ llbb\\
600575 & PowhegHerwig7EG\_NNPDF30\_AZNLO\_ZH125J\_Zinc\_MINLO\_tautau\\
\hline
\end{tabular}
\caption{List of alternative single-Higgs samples for PS uncertainties.}
\label{sec:systs:tab:systematics_singleHiggssamples_PS}
\end{table}

 
For the ttH process internal alternative weights are present in the nominal samples also to evaluate the eigentune variations for ISR and FSR variations. The Var3c eigenvariation of the A14 tune, representing the variation of the strong coupling in the initial state shower, is used to evaluate the ISR uncertainty. The FSR uncertainty is evaluated using variations of $\mu_R$ by a factor 2 up and down around the nominal value in the parton shower. 

For the ZHbb process alternative truth-level samples are used to evaluate the eigentune variations for ISR and FSR uncertainties (for the qqZH component) in the VHbb analysis and are found to be negligible as described in Ref~\cite{AlKhoury:2690042}, thus they are neglected in this analysis as well. 

%The ISR variations are found to be smaller than the parton shower alogorithmic uncertainty coming from the comparison of Pythia and Herwig and since the recommendation is to take the envelope of these effects to evaluate the total PS uncertainty the total uncertainty results in the uncertainty coming from the comparison of Pythia and Herwig thus only this one is considered. The FSR uncertainty is fund to be less than 1\% and thus it is neglected.

%For ISR the eigenvariation of the A14 tune Var1, corresponding to variations of parameters that are used in the modelling of the UE/MPI, and Var2, corresponding to variations of parameters used in the initial and final state showers, are used and summed in quadrature. The MPI variations also also used. For FSR the $\mu_R$ scale vatiations are used. The list of samples is given in Table~\ref{sec:systs:tab:systematics_singleHiggssamples_ZHbb_ISRFSR}.

%\begin{table}
%\centering
%\tiny
%\begin{tabular}{|c|c|}
%\hline
%DSID & Name\\
%\hline
%345817 & Var1Up (ISR) \\
%345811 & Var1Down (ISR) \\ 
%345829 & Var2Up (ISR) \\
%345823 & Var2Down (ISR) \\ 
%345793 & MPIUp (MPI) \\
%345787 & MPIDown (MPI) \\
%345805 & RenUp (FSR) \\
%345799 & RenDown (FSR)\\
%\hline
%\end{tabular}
%\caption{List of alternative ZHbb truth-level samples for ISR and FSR uncertainties.}
%\label{sec:systs:tab:systematics_singleHiggssamples_ZHbb_ISRFSR}
%\end{table}

%\textcolor{red}{To do: truth-level analysis being implemented, once done these uncertainties will be evaluated}

For the ttH process also the ME NLO matching uncertainty is evaluated comparing the nominal Powheg+Pythia8 samples to alternative aMC@NLO+Pythia8 samples. The list of alternative samples is given in Table~\ref{sec:systs:tab:systematics_singleHiggssamples_ttH_MENLO}.

\begin{table}
\centering
\begin{tabular}{|c|c|}
\hline
DSID & Name\\
\hline
346443 & aMcAtNloPythia8EvtGen\_ ttH\_ noShWe\_ dilep\\
346444 & aMcAtNloPythia8EvtGen\_ ttH\_ noShWe\_ semilep\\
346445 & aMcAtNloPythia8EvtGen\_ ttH\_ noShWe\_ allhad\\
\hline
\end{tabular}
\caption{List of alternative ttH samples for ME NLO matching uncertainties.}
\label{sec:systs:tab:systematics_singleHiggssamples_ttH_MENLO}
\end{table}

The size of the acceptance uncertainties on the normalisations are reported in Table~\ref{sec:systs:tab:systematics_singleHiggs_AcceptanceNumbers}. Normalisation uncertainties smaller than 1\% are neglected in the analysis. After taking out the normalisation effects, shape effects were checked on the PNN score distributions and found to be negligible as reported in Appendix~\ref{subsec:appendix_systs_singleHiggssysts} and therefore are not considered in the analysis.


\begin{table}
\centering
\small
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Process & HadHad  & LepHad SLT  & LepHad LTT  & Name & Description\\
\hline
ttH & -0.005,+0.005 & -0.006,+0.006 & -0.008,+0.008 & THEO\textunderscore ACC\textunderscore PDFalphas\textunderscore ttH  & PDF+$\alpha_s$ \\
ttH & -0.01,+0.01 & -0.003,+0.003 & -0.006,+0.006 & THEO\textunderscore ACC\textunderscore SCALE\textunderscore ttH  & Scales\\
ttH & -0.011,+0.011 & -0.013,+0.013 & -0.067,+0.067 & THEO\textunderscore ACC\textunderscore PS\textunderscore ttH & Parton Shower\\
ttH & -0.005,+0.005 & -0.001,+0.001 & -0.01,+0.01 & THEO\textunderscore ACC\textunderscore ISR\textunderscore ttH & ISR\\
ttH & -0.06, +0.037 & -0.051, +0.032 & -0.15, +0.055 & THEO\textunderscore ACC\textunderscore FSR\textunderscore ttH & FSR\\
ttH & -0.033,+0.033 & -0.0025,+0.0025 & -0.019,+0.019 & THEO\textunderscore ACC\textunderscore GEN\textunderscore ttH & ME NLO matching\\
ZHbb & -0.005,+0.005 & -0.006,+0.006 & -0.005,+0.005 & THEO\textunderscore ACC\textunderscore PDFalphas\textunderscore ZHbb  & PDF+$\alpha_s$\\
ZHbb & -0.018,+0.018 & -0.030,+0.030 & -0.025,+0.025 & THEO\textunderscore ACC\textunderscore SCALE\textunderscore ZHbb  & Scales\\
ZHbb & -0.12,+0.12 & -0.11,+0.11 & -0.037,+0.037 & THEO\textunderscore ACC\textunderscore PS\textunderscore ZHbb  & Parton Shower\\
ZHtautau & -0.01,+0.01 & -0.0077,+0.0077 & -0.012,+0.012 & THEO\textunderscore ACC\textunderscore PDFalphas\textunderscore ZHtautau  & PDF+$\alpha_s$\\
ZHtautau & -0.026,+0.026 & -0.022,+0.022 & -0.028,+0.028 & THEO\textunderscore ACC\textunderscore SCALE\textunderscore ZHtautau  & Scales\\
ZHtautau & -0.056,+0.056 & -0.055,+0.055 & -0.15,+0.15 & THEO\textunderscore ACC\textunderscore PS\textunderscore ZHtautau  & Parton shower\\
\hline
\end{tabular}
\caption{Relative size of single-Higgs acceptance uncertainties in the di-Higgs analysis.}
\label{sec:systs:tab:systematics_singleHiggs_AcceptanceNumbers}
\end{table}

%\begin{table}
%\centering
%\tiny
%\begin{tabular}{|c|c|c|c|}
%\hline
%Process & Size of uncertainty & Name & Description\\
%\hline
%ttH & 0.005,  & THEO\textunderscore ACC\textunderscore PDFalphas\textunderscore ttH  & PDF+$\alpha_s$ HadHad SR \\
%ttH & 0.006 & THEO\textunderscore ACC\textunderscore PDFalphas\textunderscore ttH & PDF+$\alpha_s$ LepHad SLT SR \\
%ttH & 0.01  & THEO\textunderscore ACC\textunderscore SCALE\textunderscore ttH  & scales HadHad SR \\
%ttH & 0.003 & THEO\textunderscore ACC\textunderscore SCALE\textunderscore ttH & scales LepHad SLT SR \\
%ttH & 0.005 & THEO\textunderscore ACC\textunderscore ISR\textunderscore ttH & ISR HadHad SR \\
%ttH & 0.001 & THEO\textunderscore ACC\textunderscore ISR\textunderscore ttH & ISR LepHad SLT SR \\
%ttH & +0.037, -0.06 & THEO\textunderscore ACC\textunderscore FSR\textunderscore ttH & FSR HadHad SR \\
%ttH & +0.032, -0.044 & THEO\textunderscore ACC\textunderscore FSR\textunderscore ttH & FSR LepHad SLT SR \\
%ZHbb & 0.005,  & THEO\textunderscore ACC\textunderscore PDFalphas\textunderscore ZHbb  & PDF+$\alpha_s$ HadHad SR \\
%ZHbb & 0.012 & THEO\textunderscore ACC\textunderscore PDFalphas\textunderscore ZHbb & PDF+$\alpha_s$ LepHad SLT SR \\
%ZHbb & 0.018  & THEO\textunderscore ACC\textunderscore SCALE\textunderscore ZHbb  & scales HadHad SR \\
%ZHbb & 0.097 & THEO\textunderscore ACC\textunderscore SCALE\textunderscore ZHbb &  scales LepHad SLT SR \\
%ZHtautau & 0.01  & THEO\textunderscore ACC\textunderscore PDFalphas\textunderscore ZHtautau  & PDF+$\alpha_s$ HadHad SR \\
%ZHtautau & 0.013 & THEO\textunderscore ACC\textunderscore PDFalphas\textunderscore ZHtautau & PDF+$\alpha_s$ LepHad SLT SR \\
%ZHtautau & 0.026  & THEO\textunderscore ACC\textunderscore SCALE\textunderscore ZHtautau  & scales HadHad SR \\
%ZHtautau & 0.033 & THEO\textunderscore ACC\textunderscore SCALE\textunderscore ZHtautau & scales LepHad SLT SR \\
%\hline
%\end{tabular}
%\caption{List of single-Higgs acceptance uncertainties. \textcolor{red}{To do: update table when all numbers are available (missing PS and ME)}}
%\label{sec:systs:tab:systematics_singleHiggs_AcceptanceNumbers}
%\end{table}

